The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-06-27 paper/iphas-dr2-arxiv.tex
arxiv version of paper

The observations included in this release
achieve a median seeing of 1.1 arcsec
and $5\sigma$-depths of $r=21.2\pm 0.5$, $i=20.0\pm 0.3$, and \ha$=20.3\pm 0.3$.
The global calibration and photometric repeatability
are found to be accurate at the level of $0.03$ mag (rms),
providing a significant improvement over the 
previous data release.
The source catalogue specifies the best-available
single-epoch astrometry and photometry
for 219~million unique sources.
To support its exploitation, we provide a list of recommended quality criteria
that will permit the selection of objects with reliable colours from 
the catalogue.  The closing demonstrations highlight the use of the 
survey's unique $(r-\ha,\ r-i)$ diagram for characterising stellar populations
and selecting emission-line objects.  More comprehensive applications of IPHAS
can be found in the works of \citet{Sale2014}, which applies DR2 to the problem
of 3D extinction mapping, and of Sabin et al (in preparation), where the results of a search
of the image database for new planetary nebulae is presented.

>>>>

The observations included in this release
achieve a median seeing of 1.1 arcsec
and $5\sigma$-depths of $r=21.2\pm 0.5$, $i=20.0\pm 0.3$, and \ha$=20.3\pm 0.3$.
The global calibration and photometric repeatability
are found to be accurate at the level of $0.03$ mag (rms),
providing a significant improvement over the 
previous data release.
The source catalogue specifies the best-available
single-epoch astrometry and photometry
for 219~million unique sources.
To support its exploitation, we provide a list of recommended quality criteria
that will permit the selection of objects with reliable colours from 
the catalogue.  The closing demonstrations highlight the use of the 
survey's unique $(r-\ha,\ r-i)$ diagram for characterising stellar populations
and selecting emission-line objects.  More comprehensive applications of IPHAS
can be found in the works of \citet{Sale2014}, which applies DR2 to the problem
of 3D extinction mapping, and of Sabin et al (submitted), where the results of a search
of the image database for new planetary nebulae is presented.
